{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-20 bmvc_review.tex
Text Edited

Table \ref{table:Comparison_to_LCT} presents the performance of
different combinations of the proposed algorithm. In short, we
empirically verified that \textit{E}nKCF is an optimal combination in
terms of tracking accuracy and run-time performance. We could achieve
4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$ at every
frame, but this combination wills sacrifice run-time performance 317
fps.  To be more specific, we employ $R_{s}$ and $R_{t}^{L}$ or
$R_{t}^{S}$ to run them in every frame in a similar way to the
multiple correlation filter framework of the LCT tracker
\cite{ma2015long}. Running another filter, $R_{t}^{L}$ or $R_{t}^{S}$,
in the {\it E}nKCF framework not only boosts run-time performance but
also increases accuracy. Lastly, we run $R_{L}$, $R_{t}^{S}$ and
$R_{s}$ in every frame.  $R_{t}^{S}$ uses the translation estimated by
$R_{t}^{L}$ to update translation and $R_{s}$ uses the final
translation estimation given by $R_{t}^{S}$ to update the
scale. Interestingly, running two complementary translation filter
results in significant improvement at the cost of decreased run-time
performance. In summary, running two (complementary) translation
filters and a scale filter as {\it E}nKCF not only increases run-time
performance but also offers more accurate tracker than the baseline
method with one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations on different combinations of the KCFs for UAV123
  dataset. We removed the particle filter from this experiment. The
  $2^{nd}$ method fliped the way of deploying $R_{t}^{L}$ and
  $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$ method removed
  $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $3^{th}$ one
  removes $R_{t}^{L}$. {\it Burak: $3^{th}$ and $3^{th}$?} The methods
  marked with "*" run the filters on every frame in the listed
  order. The LCT tracker \cite{ma2015long} runs a translation and
  scale filter in every frame (similar to the method at the $6^{th}$
  column {\it Burak: Not in $7^{th}$?} and couples a re-detection
  method to perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}

For the $UAV123$ dataset, we also evaluated the performance of the
{\it E}nKCF with and without the particle filter. In particular, we
use 50 sequences labeled as no abrupt camera motion in the dataset. To
evaluate the robustness of particle filter, we add noise, drawn from a
uniform distribution ($[-20,20]$), to the translation estimations of
the KCFs. In these settings, the {\it E}nKCF with particle filter
achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it
  E}nKCF by $6.32\%$. {\it Burak: the baseline here is the one without
  particle filter?} In summary, with the removal of global camera
motion, the integration of particle filter into the {\it E}nKCF as
shown in fig.~\ref{Workflows} further improved the results.

>>>>

Table \ref{table:Comparison_to_LCT} presents the performance of
different combinations of the proposed algorithm. In short, we
empirically verified that \textit{E}nKCF is an optimal combination in
terms of tracking accuracy and run-time performance. We could achieve
4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$ at every
frame, but this combination wills sacrifice run-time performance 317
fps.  To be more specific, we employ $R_{s}$ and $R_{t}^{L}$ or
$R_{t}^{S}$ to run them in every frame in a similar way to the
multiple correlation filter framework of the LCT tracker
\cite{ma2015long}. Running another filter, $R_{t}^{L}$ or $R_{t}^{S}$,
in the {\it E}nKCF framework not only boosts run-time performance but
also increases accuracy. Lastly, we run $R_{L}$, $R_{t}^{S}$ and
$R_{s}$ in every frame.  $R_{t}^{S}$ uses the translation estimated by
$R_{t}^{L}$ to update translation and $R_{s}$ uses the final
translation estimation given by $R_{t}^{S}$ to update the
scale. Interestingly, running two complementary translation filter
results in significant improvement at the cost of decreased run-time
performance. In summary, running two (complementary) translation
filters and a scale filter as {\it E}nKCF not only increases run-time
performance but also offers more accurate tracker than the baseline
method with one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations on different combinations of the KCFs for UAV123
  dataset. We removed the particle filter from this experiment. The
  $2^{nd}$ method fliped the way of deploying $R_{t}^{L}$ and
  $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$ method removed
  $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $4^{th}$ one
  removes $R_{t}^{L}$. {\it Burak: $3^{th}$ and $3^{th}$?} {\it YoungWoo : I meant to say $4^{th}$} The methods
  marked with "*" run the filters on every frame in the listed
  order. The LCT tracker \cite{ma2015long} runs a translation and
  scale filter in every frame (similar to the methods at the $7^{th}$ and $8^{th}$
  columns) {\it Burak: Not in $7^{th}$?} {\it YoungWoo: I meant to say $7^{th}$ and $8^{th}$} and couples a re-detection
  method to perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}

For the $UAV123$ dataset, we also evaluated the performance of the
{\it E}nKCF with and without the particle filter. In particular, we
use 50 sequences labeled as no abrupt camera motion in the dataset. To
evaluate the robustness of particle filter, we add noise, drawn from a
uniform distribution ($[-20,20]$), to the translation estimations of
the KCFs. In these settings, the {\it E}nKCF with particle filter
achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it
  E}nKCF by $6.32\%$. {\it Burak: the baseline here is the one without
  particle filter?} {\it YoungWoo : Yes, the baseline is the one without Particle Filter.} 
In summary, with the removal of global camera
motion, the integration of particle filter into the {\it E}nKCF as
shown in fig.~\ref{Workflows} further improved the results.
